---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%", 
  message = FALSE, 
  warning = FALSE
)
```

# tornado

<!-- badges: start -->
<!-- badges: end -->

The goal of tornado is to load the data of tornadoes in United States in 1950-2022 and visualize with shiny. 
The package includes the tornado dataset and a shiny app to visualize the data. The pkgdown site is available [here](https://etc5523-2024.github.io/assignment-4-packages-and-shiny-apps-joanna1016ma/).

## Installation

You can install the development version of tornado from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("ETC5523-2024/assignment-4-packages-and-shiny-apps-joanna1016ma/tornado")

# or
# install.packages("devtools")
devtools::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-joanna1016ma/tornado")
```

## Example

This is a basic example which shows you how to visualize the tornado magnitude counts of each level:

```{r example}
library(tornado)
library(tidyverse)

## Histogram example
tornados |> 
  ggplot(aes(x = mag)) + 
  geom_histogram()

```
